|

### 2020-04-27 paper/Manuscript.Rmd
CRAN spell check

1. During writing, maintain a plain-text `.bib` file with the BibTeX references for all citations.
    + You can make this file by hand; e.g., Figure \@ref(fig:scholarbib) shows how to obtain a BibTeX reference from Google Scholar; simply copy-paste each reference into the `.bib` file
    + You can export a `.bib` file from most reference manager programs; the free, open-source reference manager [Zotero](https://www.zotero.org/download/) is excellent and user-friendly, and highly interoperable with other commercial reference managers. [Here](https://christopherjunk.netlify.com/blog/2019/02/25/zotero-rmarkdown/) is a tutorial for using Zotero with Rmarkdown.
2. To cite a reference, use the `citekey` - the first word in the BibTeX entry for that reference. Insert it in the Rmarkdown file like so: `@yourcitekey2020`. For a parenthesized reference, use `[@citekeyone2020; @citekeytwo2020]`. For more options, see the [Rmarkdown cookbook](https://bookdown.org/yihui/rmarkdown-cookbook/bibliography.html).
3. To indicate a *non-essential* citation, mark it with a double at-symbol: `@nonessential2020`.
4. When Knitting the document, adapt the `knit` command in the YAML header.  
  `knit: worcs::cite_all` renders all citations, and  
  `knit: worcs::cite_essential` removes all *non-essential* citations.
5. Optional: To be extremely thorough, you could make a "branch" of the Github repository for the print version of the manuscript. Only in this branch, you use the function `knit: worcs::cite_essential`. The procedure is documented in [this tutorial](http://rstudio-pubs-static.s3.amazonaws.com/142364_3b344a38149b465c8ebc9a8cd2eee3aa.html).

@@

<!--
3. Write conceptual preregistration
* https://osf.io/zab38/wiki/home/ Templates of OSF Registration Forms
* R package prereg
* mention other examples and cite van 't Veer, A. E., & Giner-Sorolla, R. (2016). Pre-registration in social psychology---A discussion and suggested template. Journal of Experimental Social Psychology, 67, 2--12. doi: 10.1016/j.jesp.2016.03.004
3. Commit, push, and tag th as preregistration
Preregistration: tag on github
https://stackoverflow.com/questions/18216991/create-a-tag-in-a-github-repository

@@

1. Create a new Private repository on github, and copy the repository link to the clipboard. The link will look like https://github.com/yourname/yourrepo.git
2. In RStudio, click File > New Project > New directory > WORCS Project Template
    a. Paste the GitHub Repository address in the textbox
    b. Keep the checkbox for `renv` checked if you want to document all dependencies (recommended). The only reason not to do this is if you have dependencies outside of the R environment, or if you are using a more comprehensive solution for computational reproducibility, e.g., @peikertReproducibleDataAnalysis2019.
    c. Select a preregistration template
    d. Click Open in new session, and Create project
3. Write the preregistration `preregistration.Rmd`
4. In the top-right corner of RStudio, select the Git tab, select the checkboxes next to all files, and click the Commit button. Write an informative message for the commit, e.g., "Preregistration", again click Commit, and then click the green Push arrow to send your commit to GitHub
5. Go to the GitHub repository for this project, and tag the Commit as a preregistration
6. Optional: Render the preregistration to PDF, and upload it to AsPredicted.org or OSF.io as an attachment
7. Optional: Add study Materials (to which you own the rights) to the repository. It is possible to solicit feedback (by opening a GitHub Issue) and acknowledge outside contributions (by accepting Pull requests)

>>>>

1. During writing, maintain a plain-text `.bib` file with the BibTeX references for all citations.
    + You can make this file by hand; e.g., Figure \@ref(fig:scholarbib) shows how to obtain a BibTeX reference from Google Scholar; simply copy-paste each reference into the `.bib` file
    + You can export a `.bib` file from most reference manager programs; the free, open-source reference manager [Zotero](https://www.zotero.org/download/) is excellent and user-friendly, and highly interoperable with other commercial reference managers. [Here](https://christopherjunk.netlify.com/blog/2019/02/25/zotero-rmarkdown/) is a tutorial for using Zotero with Rmarkdown.
2. To cite a reference, use the `citekey` - the first word in the BibTeX entry for that reference. Insert it in the Rmarkdown file like so: `@yourcitekey2020`. For a parenthesized reference, use `[@citekeyone2020; @citekeytwo2020]`. For more options, see the [Rmarkdown cookbook](https://bookdown.org/yihui/rmarkdown-cookbook/bibliography.html).
3. To indicate a *non-essential* citation, mark it with a double at-symbol: `@nonessential2020`.
4. When Knitting the document, adapt the `knit` command in the YAML header.  
  `knit: worcs::cite_all` renders all citations, and  
  `knit: worcs::cite_essential` removes all *non-essential* citations.
5. Optional: To be extremely thorough, you could make a "branch" of the GitHub repository for the print version of the manuscript. Only in this branch, you use the function `knit: worcs::cite_essential`. The procedure is documented in [this tutorial](http://rstudio-pubs-static.s3.amazonaws.com/142364_3b344a38149b465c8ebc9a8cd2eee3aa.html).

@@

<!--
3. Write conceptual preregistration
* https://osf.io/zab38/wiki/home/ Templates of OSF Registration Forms
* R package prereg
* mention other examples and cite van 't Veer, A. E., & Giner-Sorolla, R. (2016). Pre-registration in social psychology---A discussion and suggested template. Journal of Experimental Social Psychology, 67, 2--12. doi: 10.1016/j.jesp.2016.03.004
3. Commit, push, and tag th as preregistration
Preregistration: tag on GitHub
https://stackoverflow.com/questions/18216991/create-a-tag-in-a-github-repository

@@

1. Create a new Private repository on GitHub, and copy the repository link to the clipboard. The link will look like https://github.com/yourname/yourrepo.git
2. In RStudio, click File > New Project > New directory > WORCS Project Template
    a. Paste the GitHub Repository address in the textbox
    b. Keep the checkbox for `renv` checked if you want to document all dependencies (recommended). The only reason not to do this is if you have dependencies outside of the R environment, or if you are using a more comprehensive solution for computational reproducibility, e.g., @peikertReproducibleDataAnalysis2019.
    c. Select a preregistration template
    d. Click Open in new session, and Create project
3. Write the preregistration `preregistration.Rmd`
4. In the top-right corner of RStudio, select the Git tab, select the checkboxes next to all files, and click the Commit button. Write an informative message for the commit, e.g., "Preregistration", again click Commit, and then click the green Push arrow to send your commit to GitHub
5. Go to the GitHub repository for this project, and tag the Commit as a preregistration
6. Optional: Render the preregistration to PDF, and upload it to AsPredicted.org or OSF.io as an attachment
7. Optional: Add study Materials (to which you own the rights) to the repository. It is possible to solicit feedback (by opening a GitHub Issue) and acknowledge outside contributions (by accepting Pull requests)

### 2020-04-27 paper/notes.Rmd
CRAN spell check

Post-publication review: OSF has comments feature; github issues

@@

Adequate citation of statistical software is important, because open source software is an important type of research output for statisticians. An easy way to cite all packages used is to write an APA-style paper in Rmarkdown using the `papaja` package. Cite all packages with the function `cite_r()`, and add the BibTeX entries for these packages to the reference file using `r_refs("filename.bib")`. However, it might not be feasible or desireable (e.g., due to journal limits on the number of references) to cite all packages. Therefore, a more practical solution might be to cite only the most important packages. The citation for each package can be obtained by running `citation("packagename")`. If this approach is combined with a fully reproducible R-environment (using the `renv` package) and code sharing (e.g., on Github or the OSF), then the full list of package dependencies is documented automatically in the `.lock` file.

>>>>

Post-publication review: OSF has comments feature; GitHub issues

@@

Adequate citation of statistical software is important, because open source software is an important type of research output for statisticians. An easy way to cite all packages used is to write an APA-style paper in Rmarkdown using the `papaja` package. Cite all packages with the function `cite_r()`, and add the BibTeX entries for these packages to the reference file using `r_refs("filename.bib")`. However, it might not be feasible or desireable (e.g., due to journal limits on the number of references) to cite all packages. Therefore, a more practical solution might be to cite only the most important packages. The citation for each package can be obtained by running `citation("packagename")`. If this approach is combined with a fully reproducible R-environment (using the `renv` package) and code sharing (e.g., on GitHub or the OSF), then the full list of package dependencies is documented automatically in the `.lock` file.
